% Formatting -----------------------------------
% Setting the page numbers to be arabic 
\pagenumbering{arabic}

\fancyfoot{}

\fancyfoot[LE]{\colorbox{urban-footergray}{\makebox(0.2, 0.12)[r]{\fontsize{7.5}{0}\selectfont\bfseries{\MakeUppercase{}\hspace{0.2in}}}}\colorbox{urban-gold}{\makebox(0.2, 0.12)[c]{\fontsize{7.5}{0}\selectfont\bfseries{\MakeUppercase\thepage}}}\colorbox{urban-footergray}{\makebox(5.64, 0.12)[r]{\fontsize{7.5}{0}\selectfont\bfseries{\MakeUppercase{TEXT TEXT}\hspace{0.2in}}}}}

\fancyfoot[RO]{\colorbox{urban-footergray}{\makebox(5.64, 0.12)[l]{\fontsize{7.5}{0}\selectfont\bfseries{\hspace{0.2in}\MakeUppercase{TEXT TEXT}}}}\colorbox{urban-gold}{\makebox(0.2, 0.12)[c]{\fontsize{7.5}{0}\selectfont\bfseries{\MakeUppercase\thepage}}}\colorbox{urban-footergray}{\makebox(0.2, 0.12)[r]{\fontsize{7.5}{0}\selectfont\bfseries{\MakeUppercase{}\hspace{0.2in}}}}}
% Formatting -----------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Report %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\part{Report Title Here in Title Case (Heading 1 style)}

Body Text style for first paragraph.

Body Text First Indent style for subsequent paragraphs. \textcolor{red}{To add an endnote, use the Insert Endnote function. Endnotes will automatically appear in the Notes section after the appendixes.}\endnote{Endnotes inserted in the executive summary, main report, and appendixes will all display here if section breaks are used correctly.} 

\section{First-Level Heading in Title Case (Heading 2 style)}

Body Text style for first paragraph under a heading.

Body Text First Indent style for all subsequent paragraphs.
\begin{itemize}
    \item Bulleted List style for bulleted lists.
    \item Another bullet using Bulleted List style.
    \begin{itemize}
        \item Bulleted List 2 style for second-level bulleted items under a numbered or bulleted list item.
        \item Another item using Bulleted List 2 style.
    \end{itemize}
    \item Another bullet using Bulleted List style.\\
    Indented Text style for ordinary paragraphs under a numbered or bulleted list item.
\end{itemize}

\noindent Body Text First Indent style for all subsequent paragraphs.

\begin{enumerate}
    \item Numbered List style for numbered lists
    \begin{enumerate}
        \item Numbered List 2 style for second-level lettered items under a numbered or bulleted list item.
        \item Another paragraph using Numbered List 2 style.
    \end{enumerate}
    \item Another item using Numbered List style.\\
    Indented Text style for ordinary paragraphs under a numbered or bulleted list item.
\end{enumerate}

\noindent Body Text First Indent style for all subsequent paragraphs.

\subsection{Second-Level Heading in Title Case (Heading 3 style)}

\indent Body Text style for first paragraph under a heading.

\subsubsection{Third-level heading; all caps is built into style (heading 4 style)}

Body Text style for first paragraph under a heading.

\fourthsub{Fourth-level headings are run into the text.} Select the first clause or sentence of your paragraph, then apply the Heading 5 (D) style. 

Pull Quote style for pull quotes.

---Pull quote attribution in sentence case

Body Text First Indent style for all subsequent paragraphs.

\block{Block Text style for longer (100+ words) quotes and excerpts.}

\newpage
\part{Reference Styles}

\section{Reference Styles for Urban Products}

\subsection{Blog posts (cite in notes, not reference list)}

\subsection{Policy debates (cite in notes, not reference list)}

\textbf{The entire debate:}

\textbf{One post in the debate:}

\cite{Ful83}